**fabryka**

### 2025-07-15 fabryka_pci/article.Rmd
correction of fabryka article and shiny application after first round of review in PCI archaeology

-   use fabryka online: <https://marchaeologist.shinyapps.io/fabryka/> \smallbreak
-   source code: <https://github.com/marchaeologist/fabryka/tree/main> \smallbreak
-   Report bugs or any request: <https://github.com/marchaeologist/fabryka/issues> \smallbreak
-   github reprository doi of fabryka: <https://doi.org/10.5281/zenodo.15881625> \smallbreak
-   Zenodo repository of this article: <https://doi.org/10.5281/zenodo.15879462> \bigbreak

>>>>

-   use fabryka online: <https://marchaeologist.shinyapps.io/fabryka/> \smallbreak
-   source code: <https://github.com/marchaeologist/fabryka/tree/main> \smallbreak
-   Report bugs or any request: <https://github.com/marchaeologist/fabryka/issues> \smallbreak
-   github reprository doi of fabryka: <https://doi.org/10.5281/zenodo.15909666> \smallbreak
-   Zenodo repository of this article: <https://doi.org/10.5281/zenodo.15880861> \bigbreak
